The 2018 heatwave and its implications on ozone induced damage on vegetation in a subarctic climate

### 2020-10-09 VegOzone.tex
Add note about DO3SE parameter list which shall go to supplement.

{\bf TODO: Some general words about DO3SE model?}

@@

{\bf TODO: Model results for natural and semi-natural vegetation (birch, pine, clover, tobacco(?))}
\begin{itemize}
\item climatological ozone impact
\item 2018
\item 2019
\end{itemize}

>>>>

{\bf TODO: Some general words about DO3SE model}

\subsection{Model parameters}
A comprehensive list of model parameters used in this study is found in Supplement~X.

@@

{\bf TODO: Model results for natural and semi-natural vegetation (birch, pine, grassland)}
\begin{itemize}
\item climatological ozone impact
\item 2018
\item 2019
\end{itemize}
